Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
$\CMon569XZilmsenriched presheaf.
CMon-enriched functors also preserve bilinear composition.

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-objects
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, we have that $F$
satisfies:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{FY,FX}$
\item $F(f + g) = Ff + Fg$
\end{itemize}

>>>>

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-objects
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
and also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.
